BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-04-25 manuscript/CoverLetter.rmd
part of letter to editor; v difficult to not be cheeky given why this actually exists...

@@

>>>>

While a variety of software tools exist for interacting with accessioned herbarium data, fewer are dedicated towards accessioning material. 
And even fewer of these tools are intended for an actual collector to interact with. 
This isn't surprising, as the number of collectors who are not curators has decreased, and the barrier to entry for both activities is a degree of eccentricity and particularity. 
Unfortunately, the particularity of curators often makes depositing specimens to herbaria a challenging task for collectors. 
A common challenge for collectors, especially those who work on large projects implemented by federal agencies, such as germplasm collection (e.g. Seeds of Success), ecological monitoring (e.g. National Wetland Condition Assessment, and Assess, Inventory, and Monitor), are the needs to satisfy the particularities of multiple curators simultaneously.

Fortunately, I have been scolded by many curators over the last decade (and on occasion even received constructive criticism), and built up a wide knowledge of quirks to cater to. 
As a manager of young botanists for the last handful of years, I have insisted on maintaining a degree of separation between my employees and curators, in hopes that the small glimmer of hope which the youths have for the profession isn't extinguished. 
To assist myself in running quality control checks, for both mine and their collections, I developed a wind range of functions which help meet a broad set of interests; in fact the package with all of these tools have been rolled into - BarnebyLives - has 30 user facing functions, at least another 10 internals, and 8 data sets. 
The package is used to both access commonly mistaken data, perform an array of spell checks, offer botanists more recently applied scientific names, and export data and write labels for them. 
Curators across roughly 15 institutes have been very impressed by the results, while one or two may just dislike me as individual.

@@

\newpage

Reviewers:

Shelly Gaynor mlgaynor@umich.edu 
R package author extraordinaire, multiple thorough publications with APPS for software notes, and (former?) member of iDigBio team.

Ben Legler blegler@uwyo.edu 
Database administrator and creator of two large herbaria consortia, field botanist extraordinaire.

Jason Alexander jason_alexander@berkeley.edu 
I don't actually know Jason, word from our mutuals is he knows his stuff and this should be within his wheelhouse.

Charles Davies cdavis@oeb.harvard.edu 
Yeah, this one is a bit of a stretch, but I need to suggest four reviewers. 
I doubt he has time for this, but maybe one of his graduate students would be interested. 
Reasoning: general using herbaria specimens in ecology at global scale perspectives, as well as active taxonomist.
